\documentclass[10pt]{article}
\usepackage{hyperref}
\usepackage[hmargin=1.25cm, vmargin=0.55cm]{geometry}
\begin{document}
\title{Brief Statement}
\author{Jamie Ryan \\ 
Mullard Space Science Laboratory \\
University College London \\
Surrey, RH13 6NL, UK\\
\href{mailto:jamie.ryan.14@ucl.ac.uk}{jamie.ryan.14@ucl.ac.uk} \\
\date{\today}
}
\maketitle



To understand the mechanisms that control a large range of phenomena, from sunquakes to coronal mass ejections, we
need to understand how energy moves through the chromosphere. The majority of the energy released by a flare is deposited
in the lower solar atmosphere in the form of radiation. The radiative processes associated with impulsive flares span almost
the entire range of wavelengths, including ultraviolet, white light continuum, x-rays, gamma rays and microwaves. This
release of energy in the lower atmosphere is highlighted by hard x-ray footpoints in the chromosphere, which occur simul-
taneously, giving hints that accelerated charged particles have an important part to play in the radiative energy deposition
process. Accelerated charged particles are an indicator of reconfiguring magnetic fields during the flare, with the motions
of footpoint locations being strongly tied to the location of magnetically driven particle beams. The radiative emissions
mentioned are usually within the confines of flare ribbons, which are an important observational tool as they are another
indicator of magnetic structure reconfiguration, and are thought to connect directly to coronal magnetic reconnection sites.
Magnetic energy is somehow transported from high altitudes in the solar corona, back down to the lower atmosphere, in
such a way as to reach the photosphere before being completely dissipated, this is not a mechanism that is fully understood,
especially in the UV and optical wavelengths, which brings us to the focus of my research. \\

My PhD is primarily based on investigating how energy is released and transported as a result of solar flare eruptions, in particularly the lower atmospheric signature of the process, and the possible mechanisms for the production of local acoustic waves in the photosphere and sub-photosphere. IRIS provides invaluable data for this pursuit and being in the first year of my PhD, I believe that this is the perfect time to enrol on this workshop. The chromosphere is a very dynamic region due to the changing influences (on the residing plasma) of gas and magnetic pressure. This part of the solar atmosphere effectively controls how energy is released into the upper layers, such as the transition region and corona, and how it is filtered back down to the photosphere. In order to grasp the physics governing the observed motions of plasma within the chromosphere, it is vital to understand the physical parameters dictating such events; IRIS has the unique ability to provide both imagery and spectroscopic data needed to achieve this goal. \\

IRIS is capable of capturing information from the Sun in exquisite spatial and temporal resolution, allowing the morphologies and physical properties of features to be more accurately observed. The ability to couple intensity maps with spectroscopic observations means that the tracking of a feature through space and time can be linked directly to particular line shapes, spectral widths and displacements, allowing diagnostics of the physical parameters associated with energy deposition processes, such as waves and shocks, to become accessible. For this reason, the optically thick MgII h and k lines included in the IRIS data should prove to be a vital tool for my research, however, interpreting this spectroscopic data is a non-trivial matter, hence, inclusion on the IRIS-4 Workshop is crucial for helping in the understanding of how to work with such data, and will prove critical for the success of my research.\\
\\

Thank you for your consideration



  


\end{document}
