%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%Progenitors of sunquakes%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Sunquake Progenitors}
%list and explain current theories of sunquake generation
%making sure to highlight the different observables that can identify each mechanism, eg wlf = evidence of radiative backwarming  

The progenitors of sunquakes are still unknown and as a result this is an exciting area of research with discoveries still to be made. The general consensus, in terms of valid mechanisms that could cause this phenomenon is an area of contention, however the following progenitors are thought to be at least partly responsible and in reality it may be a combination of these processes: 

\begin{itemize}
\item Radiative backwarming \citep{1989SoPh..124..303M} is a mechanism which takes into account the fact that the majority of sunquake events coincide with white light emission from the lower atmosphere. First put forward by \cite{2005ApJ...630.1168D}, the idea is that high energy electrons and photons penetrate the chromosphere, impulsively heating the photosphere producing white light emission. This causes a pressure wave which propagates into the sub-photosphere generating an acoustic wave. 
     
\item Sudden magnetic field reconfiguration \citep{2008ASPC..383..221H} when the field relaxes to a more horizontal alignment it can impart a force on the photosphere resulting in acoustic waves in the sub-photosphere. The field has to reconfigure in an impulsive manner to generate sufficient force to induce seismic waves. 

\item Shocks \citep{1998Natur.393..317K} are the result of explosive ablation of chromospheric material caused by heating due to collisions with energetic particles. The generated shock travels down through the lower atmosphere impacting the photosphere and sub-photosphere generating acoustic waves.  

\item Direct proton collision is a method by which an energetic beam of protons makes it down into the lower atmospheric layers of the Sun and deposits energy directly into the photosphere, which generates acoustic waves. Observations by \cite{2007ApJ...664..573Z} show flares with sunquakes associated with $\gamma$-rays which are an indicative signature of accelerated energetic protons.
\end{itemize}
